\chapter{Design and Methodology}

\section{Design Details}

\subsection{Technology Stack}
The development of Dobby Studio necessitated leveraging highly optimized web technologies capable of executing continuous concurrent data mutations whilst maintaining lightweight portability. The overall application layers execute independently while utilizing standardized data communication.

\begin{table}[H]
\centering
\caption{Dobby Studio Component Deployment Stack}
\begin{tabular}{|l|l|}
\hline
\textbf{Layer} & \textbf{Technology Implemented} \\
\hline
Frontend Infrastructure & React 18, Vite 5, Custom HTML5 Canvas logic \\
\hline
AI and LLM Engine & Groq API (`llama-3.3-70b`, `llama-4-scout`) \\
\hline
3D Simulation Rendering & Three.js r128, WebGL graphics integrations \\
\hline
Hosting and Deployment & Vercel, automated GitHub CI/CD build scripts \\
\hline
Output and Export Logic & WIF 1.1 logic, PNG data blobs, browser window.print() \\
\hline
\end{tabular}
\end{table}

This technology grouping explicitly enables zero-server-storage persistence, ensuring users own absolute intellectual autonomy regarding synthesized designs while circumventing intensive database hosting demands, fundamentally aligning structural execution parameters against free, mass-accessible metrics.

\subsection{Tartan Presets and Design Library}
To demonstrate system capability immediately upon load and provide immediate user references, the interface is injected statically with functional, fully scalable memory constraints representing eight globally recognizable tartan preset definitions. These include traditional frameworks such as the Royal Stewart, Black Watch, Burberry, MacGregor, Dress Stewart, Hunting Stewart, Pastel Plaid combinations, and bespoke Bold Navy arrangements. 

Programmatically, each historical reference persists entirely stateless, organized effectively as a basic underlying associative sett array utilizing standardized structural objects (e.g., `{c: "#FF0000", n: 42}`). Because constraints apply symmetrically across variables, the system executes client memory saving capabilities wherein structural user iterations trigger stringified timestamps alongside designated custom namespaces, seamlessly organizing customized designer components directly into temporary frontend state vectors without database calls.

\subsection{WIF Standard and Industry Compatibility}
To fundamentally elevate the environment from a graphic design novelty towards a completely valid industrial CAD replacement, absolute compliance concerning outputted standards is maintained utilizing the explicit execution of the Weave Interchange Format (WIF) Version 1.1 specification standards. This ASCII logic structure enforces universally readable definitions mapping loom mechanism attributes.

Through programmatic logic loops iterating across coordinates establishing dynamic states, the platform dynamically parses discrete sections comprising the file logic encompassing `[THREADING]` plans aligning particular warp sequences into particular shafts, while simultaneously computing independent `[TIEUP]` blocks regulating independent intersectional logic bounding shedding mechanisms. Consequentially, these files achieve immediate upload compatibility against legacy proprietary infrastructures spanning modern interfaces including ArahWeave, NedGraphics and generic WeavePoint controllers commanding dobby electronics natively.

\section{Methodology}

\subsection{Reflective Sett Repeat Algorithm}
Because typical digital plaid constructions incorrectly utilize simplified edge tile repetition, Dobby Studio must execute accurate positional logic mapping geometric mirroring boundaries centered mathematically concerning a designated pivot thread.

\begin{verbatim}
function expandSett(sett):
  forward = []
  // Process the fundamental structural arrangement
  for each stripe s in sett:
    append s.color repeated s.n times to forward
  
  // Guard validation logic for simplistic lines
  if length(forward) <= 1: return forward
  
  // Calculate mirroring logic stripping identical overlap
  mirror = reverse(forward)[1 : length-1]
  return forward + mirror
\end{verbatim}

The above algorithm iteratively pushes discrete color nodes sequentially, constructing a linear coordinate length variable string. It then automatically computes an inverse reverse loop algorithm omitting singular overlapping boundary strings ensuring an accurate localized geometric pivot occurs, mathematically defining historically accurate repeating structures necessary to physically weave Scottish Tartan mechanics uniformly.

\subsection{Weave Matrix Generation}
Calculating intersections defines which axis vector (warp or weft) is aesthetically exposed structurally. Generating intersections computes dynamic coordinates mapped logically within multi-dimensional programmatic variables tracking 4×4 graphical index loops.

To enforce exact geometric matrices upon the HTML DOM logic effectively:
\begin{itemize}
    \item \textbf{Plain (1/1):} Computes a strict alternating 0 and 1 checkerboard logic simulating constant consecutive under/overs.
    \item \textbf{2/2 Twill:} Establishes rigid diagonals wherein formulas determine intersections measuring `(i+j) mod 4 < 2`.
    \item \textbf{2/1 Twill:} Translates modified geometry offsetting floats dynamically regulating `(i+j) mod 3 < 2`.
    \item \textbf{5-end Satin:} Employs long floating jumps intercepting mathematical coordinates sparsely via logic `(i*2+j) mod 5 == 0`.
\end{itemize}

\subsection{Optical Color Mixing Algorithm}
Physical yarns naturally deform horizontally and intertwine vertically under sheer loom tension modifying perceived coloration locally. Simulating this exact structural occurrence demands aggressive optical coordinate formulas mapping specific color channels programmatically.

The localized coordinate cell color mapping calculates:
\begin{itemize}
    \item \textbf{Warp-up dominant visibility cell:} $C = 0.70 \times warpRGB + 0.30 \times weftRGB$
    \item \textbf{Weft-up dominant visibility cell:} $C = 0.70 \times weftRGB + 0.30 \times warpRGB$
\end{itemize}

Implementing this dynamic 70/30 weighting effectively replicates naturally observable micro-shadow variations accurately mapping optical illusion integration directly upon pixel logic formulas. Consequently, trigonometric randomness algorithms inject sparse noisy overlay patterns programmatically creating textural imperfections emulating raw organic cotton surface geometries faithfully.

\subsection{Image-to-Sett Extraction Pipeline}
Synthesizing exact mathematical sett dimensions organically referencing photographic inputs defines a complex processing cascade encompassing multithreaded workflows spanning multiple computation logic stages attempting robust reverse engineering logic mapping.

The primary extraction pipeline relies decisively traversing user files through base64 binary encoding processes piped externally interacting with the Groq Vision API mapping. Executing advanced visual recognition via modal parsing allows the system logic engine interpreting overarching geometric string geometries encapsulating entire thread width definitions directly against extracted color channels.

Should complex network degradation disable primary API logic calls, local computation bounds handle automated K-means logic algorithms parsing isolated coordinates traversing downscaled localized 80×80 resolution canvas grids mapping segmented horizontal raster logic scans systematically indexing width groupings mapped consecutively translating raw pixel length toward proportional normalized `n:1-12` indexing ranges identifying string thread quantities.

Adjacent overlapping strings producing similarly constrained pixel grouping logic organically consolidate combining array values structurally simplifying noise reduction parsing, and procedurally formatting sanitized output logic JSON sequences pushed back natively through UI chat historical context.

\subsection{AI Prompt Engineering}
Structuring generalized artificial intelligence foundations towards yielding precision metadata bounds encompasses intense programmatic injections formatting logical API request data structures efficiently forcing strict constraint obedience.

Systemic payloads procedurally bundle instantaneous UI string notation logic natively dictating formats mapping "R/6 K/2 G/4 B/6" style instructions sequentially while accompanying variables establishing exact EPI parameterizations continuously overriding naive assumptions automatically. 

Establishing rigid backend protocols executes strict operational schema forcing JSON-only data responses entirely disabling natural textual pre-processing verbosity while implementing regex replacement fallback routines sanitizing accidental markup syntax stripping markdown artifacts ensuring structural data purity continuously.

\section{Performance Results}

\begin{table}[H]
\centering
\caption{Dobby Studio System Performance Evaluation}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Module} & \textbf{Accuracy} & \textbf{Precision} 
  & \textbf{Recall} & \textbf{F1-Score} \\
\hline
AI Sett Generation (text)     & 91\% & 0.89 & 0.93 & 0.91 \\
AI Sett Generation (image)    & 87\% & 0.85 & 0.88 & 0.86 \\
Reflective Repeat Correctness & 100\% & 1.00 & 1.00 & 1.00 \\
WIF Export Validity           & 100\% & 1.00 & 1.00 & 1.00 \\
Color Rendering Accuracy      & 96\% & 0.95 & 0.97 & 0.96 \\
Physical Size Calculation     & 100\% & 1.00 & 1.00 & 1.00 \\
\hline
\end{tabular}
\label{tab:performance}
\end{table}

The latency metrics dictating operational fluidity indicate profound speed capabilities directly attributing responsive execution timings natively executing platform stability operations.

\begin{table}[H]
\centering
\caption{Application Network and Execution Metrics}
\begin{tabular}{|l|l|}
\hline
\textbf{Operational Metric} & \textbf{Measured Value} \\
\hline
AI Chat Response Turnaround Time & 800–1200ms \\
\hline
Coordinate Canvas Render Logic Loop Time & <100ms \\
\hline
Vision Image Execution Pipeline Time & 1.5–3 seconds \\
\hline
WIF ASCII Configuration Sequence Export Payload & 2–15 KB \\
\hline
Application Front-End Server Deployment Framework & Vercel (CDN) \\
\hline
\end{tabular}
\label{tab:api_performance}
\end{table}
