\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

We would like to express our deepest gratitude to our project guide, Dr. Varsha Patil, for her invaluable guidance, continuous support, and constructive feedback throughout the development of Dobby Studio. Her expertise and direction were instrumental in shaping the technical and academic trajectory of this project. Furthermore, we are immensely thankful to our project coordinator, Dr. Bhagyalakshmi Mukunda, for ensuring a seamless evaluation process and providing essential resources.

We extend our sincere appreciation to Dr. Varsha Patil, our Head of Department, who created an intellectually stimulating environment for research and innovation within the Department of Artificial Intelligence and Machine Learning. We are also deeply indebted to our Principal, Dr. K Lakshmisudha, for providing the institutional infrastructure and academic freedom that allowed us to pursue this interdisciplinary endeavor at SIES Graduate School of Technology.

Lastly, we wish to thank all the faculty members whose foundational teachings in software engineering and artificial intelligence gave us the skills needed for this work. A heartfelt thanks to our parents and friends for their unwavering moral support. Developing this project was a collaborative effort, and we recognize the immense hard work put in by every member of our team to bring this vision to life.

\vspace{2cm}

\begin{flushright}
\textbf{Project Team:}\\
Ojas Neve\\
Gaurav Patil\\
Sahil Powar\\
Saachi Sawant
\end{flushright}
